A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-21 paper.tex

%\vspace{-10pt}
%\paragraph{Fields:} The BRST fields are given by:
%>>>>>>> 016a15254e190191104552713b6e9bc2dba88afb
%\begin{itemize}
%\item A gauge field $A \in \Omega^1(M;\fg)$.
%\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
%\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
%\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
%\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
%\end{itemize}
%
%<<<<<<< HEAD
%Under the $R$-symmetry $\lambda, \phi$ transform as the fundamental representations. \brian{Does this sound right?}

%\subsubsection{Holomorphic twist}
%
%Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
%The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  
%Without loss of generality we will twist with respect to a supercharge of the form 
%\[
%Q = q_+ \otimes w_1 \in S_+ \otimes W_+ .
%\]
%Such a $Q$ is preserved under the twisting homomorphism
%\[
%\MU(3) \to {\rm Spin}(6) \times \SU(2) .
%\]
%In the first component this is the homomorphism $\MU(3) \to {\rm Spin}(6)$ lifting $\U(3) \to {\rm SO}(6)$. 
%In the second component, this is the composition $\MU(3) \to \U(1) \to \SU(2)$ where the first map is $\det^{-1/2}$ and the second map is $z \mapsto \begin{pmatrix} z & 0 \\ 0 & \Bar{z} \end{pmatrix}$. 
%
%There is no twisting datum homomorphism $\alpha : U(1) \to \SU(2)$ compatible with this twisting homomorphism.
%Thus, the resulting twisted theory is only $\ZZ/2$-graded.
%
%Under the action of $\MU(3)$, the fields decompose as:
%\begin{align*}
%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3 ; \fg) \\
%\lambda & \mapsto \lambda_{0} + {B}_{1,0} + \chi + \lambda_0 \in \Omega^0(\CC^3 ; \fg) \oplus \Omega^{0,2}(\CC^3 ; \fg) \oplus \Omega^{3,0}(\CC^3 ; \fg) \oplus \Omega^{3,2}(\CC^3 ; \fg) \\
%\phi & \mapsto \nu + \psi_0 \in \Omega^0(\CC^3; K^{-1/2} \otimes U) \oplus \Omega^0(\CC^3 ; K^{1/2} \otimes U) \\
%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; K^{1/2} \otimes U) \oplus \Omega^{0,3} (\CC^3; K^{1/2} \otimes U ),
%\end{align*} 
%
%%\begin{align*}
%%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
%%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
%%\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
%%\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
%%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
%%\end{align*} 
%
%\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
%and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.  In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
%=======
\subsubsection{Holomorphic twist}
\label{sec:6dholomorphictwist}

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$\brian{Should this be $\psi \in \Omega^{0,1}(M; \Pi U\otimes K^{1/2})$?}.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{3, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 3}(M)$ the antiholomorphic volume form.  We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^3}{6} = \Omega\wedge \ol{\Omega}.\]

@@

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\brian{What's our convention for ``twisted maps?}

\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a different twisting homomorphism
\[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

With these modifications the BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \fg)[-1]$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)[1]$, $B\in\Omega^{0, 2}(M; \fg)[-1]$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)[1]$.
\item Matter bosons $\nu\in\Omega^0(M; R^*\oplus R\otimes K^{-1}[-2])$, $\phi\in\Omega^0(M; R\oplus R^*\otimes K[2])$.
\item Matter fermions $\psi\in \Omega^{1, 0}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

\subsection{\texorpdfstring{$\mc N = (1,1)$}{N=(1,1)} Super Yang-Mills Theory}

There is a 6d gauge theory with $\mc N=(1,1)$ supersymmetry obtained by dimensionally reducing the maximal super Yang-Mills theory on $\RR^{10}$ down to $\RR^6$. This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.

\vspace{-10pt}
\paragraph{Fields:} Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
\begin{itemize}
 \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.  These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e. the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.  We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
 \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
\end{itemize}

We can write the supersymmetry action here explicitly. \chris{though it isn't necessary: remove it?}

\begin{prop} \label{O6_decomposition_of_susy_prop}
After reduction to $\mr O(6)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^+)\rangle\omega(w^+,u^+) + \langle \phi^\vee, (Q^+,\lambda^-)\rangle w^+ \otimes u^- + \\&\qquad + \langle (\lambda^{+} \otimes u^+)^\vee, \sd F_A (Q^+ \otimes w^+) \rangle + \langle (\lambda^{-} \otimes u^-)^\vee, \rho(\dd \phi)(Q^+ \otimes w^+) \rangle\\
I^{(2)}(Q^+, Q^+) &= \left(\langle\lambda^{+\vee},Q^+\rangle\langle u^{+\vee}, w^+ \rangle\right)^2
\end{align*}
if $Q^+ \otimes w^+$ is an element of $S_+ \otimes W_+$, and
\begin{align*}
I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^-)\rangle\omega(w^-,u^-) + \langle \phi^\vee, (Q^-,\lambda^+)\rangle w^- \otimes u^+ + \\&\qquad + \langle (\lambda^{-} \otimes u^-)^\vee, \sd F_A (Q^- \otimes w^-) \rangle + \langle (\lambda^{+} \otimes u^+)^\vee, \rho(\dd \phi)(Q^- \otimes w^-) \rangle\\
I^{(2)}(Q^-, Q^-) &= \left(\langle\lambda^{-\vee},Q^-\rangle\langle u^{-\vee}, w^- \rangle\right)^2
\end{align*}
if $Q^- \otimes W_-$ is an element of $S_- \otimes W_-$.  In each of these expressions, we have suppressed in the notation some contractions of tensors between $W_+ \otimes W_-$ and its dual.  There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
\end{prop}

\begin{remark}
If we set $\lambda^- \otimes u^-$ and $\phi$ to zero, and consider only the action of $Q^+ \otimes w^+$, then we recover the supersymmetry action for the $\mc N=(1,0)$ pure gauge theory.  If instead we set $\lambda^+ \otimes u^+$ and $A$ to zero, and consider only the action of $Q^- \otimes w^-$ then we recover the supersymmetry action for the $\mc N=(1,0)$ pure matter theory.
\end{remark}

\vspace{-10pt}
\paragraph{Twisting data:}
In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ supersymmetry algebra.
 \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
 \begin{enumerate}
 \item Generically, $Q$ is topological.
 \item There is a degenerate locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

We already considered the holomorphic twist in the previous section: it admits the following description.

\begin{theorem} \label{6d_holo_twist_thm}
The holomorphic twist of 6d $\mc N=(1,1)$ super Yang-Mills theory is perturbatively equivalent to holomorphic BF theory on $\CC^3$ with target given by the adjoint quotient $\gg/\gg$, i.e. the theory with fields $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$.
\end{theorem}

\begin{proof}
Take the description of the holomorphically twisted theory from Theorem \ref{thm:6dholomorphictwist}, and let $U = T^*\gg$.  One identifies the resulting description as a $\ZZ$-graded theory with a cotangent theory as described in Remark \ref{6d_BF_remark}.
\end{proof}

The remaining three classes of twists are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.

\begin{theorem} \label{6d_rk11_twist_thm}
The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is perturbatively equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

\begin{theorem} \label{6d_rk22_twist_thm}
The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is perturbatively equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
\end{theorem}

\begin{proof}
We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
\end{proof}

@@

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, U \ham g)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:8dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}

>>>>

\subsubsection{Holomorphic twist}
\label{sec:6dholomorphictwist}

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
\item Matter fermions $\psi\in \Omega^{0, 1}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form. We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^3}{6}.\]

@@

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a new twisting homomorphism
\[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

With these modifications the BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \fg)[-1]$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)[1]$, $B\in\Omega^{0, 2}(M; \fg)[-1]$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)[1]$.
\item Matter bosons $\nu\in\Omega^0(M; R^*\oplus R\otimes K^{-1}[-2])$, $\phi\in\Omega^0(M; R\oplus R^*\otimes K[2])$.
\item Matter fermions $\psi\in \Omega^{0, 1}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}

The 6d $\cN=(1, 1)$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. It admits $R$-symmetry group $G_R=\Spin(4, \RR)$ under which $W_+, W_-$ are the two semi-spin representations.

Given an element $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ we denote by $W^*_{Q_\pm}\subset S_\pm$ the images of $Q$. We classify square-zero supercharges according to the ranks of these spaces:
\begin{itemize}
\item Rank $(1, 0)$ and $(0, 1)$. These automatically square to zero and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ (respectively, $\cN=(0, 1)$) supersymmetry algebra. They admit a twisting homomorphism from $\MU(3)$ and a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$.

\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle = 0$. These automatically square to zero and have 4 invariant directions. There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.

\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle \neq 0$. These automatically square to zero and are topological. Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding.

\item Rank $(2, 2)$. The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory. There is the identity twisting homomorphism $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \RR)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
\end{itemize}

The 6d $\cN=(1, 1)$ super Yang--Mills theory viewed as a $\cN=(1, 0)$ supersymmetric theory coincides with the 6d $\cN=(1, 0)$ super Yang--Mills with matter in the representation $U=T^*\fg=\fg\oplus \fg^*$. Under this isomorphism the R-symmetry group $\SU(2)\times \U(1)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SU(2)\times \SU(2)$ of 6d $\cN=(1, 1)$ super Yang--Mills. In particular, from Theorem \ref{thm:6dholomorphictwistgraded} we obtain the following statement.

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:6d11holomorphictwist}
\end{thm}

\subsubsection{Rank $(1, 1)$ partially topological twist}

We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]

Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$. Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.

\begin{thm}
The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$. Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
\end{thm}
\begin{proof}
The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.

To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$. In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}. The claim then follows from a direct comparison.
\end{proof}

Next we study the rank $(1, 1)$ topological twist. Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$. Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
\[
S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
\]
Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in \Sigma.
\label{eq:6dHodgefamily}
\end{equation}
At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.

\begin{thm}
The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:6dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}. So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills. Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
\end{proof}

\begin{cor}
The topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively trivial.
\end{cor}

\subsubsection{Rank $(2, 2)$ twist}

We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.

\begin{thm}
The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
\label{thm:6drank22}
\end{thm}
\begin{proof}
Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.

Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e. $s_+^\pm, s_-^\pm$ are all nonzero. The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.

$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$. But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.

So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$. The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
\end{proof}

@@

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, U \ham g)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}
